Is the family of sentences really a family?

### 2024-02-14 writing/SuB-paper/supplement.tex
tracking udpates from overleaf wed afternoon

\end{document}

>>>>

\section{Analysis 1 --- Estimating operator effects on projection}

    Bayesian mixed effects beta regression for the full dataset.\footnote{The analysis script can be found at \url{https://github.com/judith-tonhauser/CommitmentBankPlus/blob/main/results/main/meta-analyses/1_projection/rscripts/2_analysis-operators.R}.}\\

    \noindent\textbf{Repsonse variable:} projection ratings scaled for beta-regression to transform from closed unit interval $[0,1]$ to open unit interval $(0,1)$,
    % using method used in \cite{degen_are_2022}, from \cite{smithson_better_2006}, for proportional data.
    $$y' = \frac{y * (n - 1) + 0.5}{n}$$

    \noindent\textbf{Fixed effect:} operator (modal, negation, question, conditional; with reference level: modal)\\

    \noindent\textbf{Random effects:}

\section{Analysis 2 --- Estimating operator effects for each predicate}

    Bayesian mixed effects beta regression for the each subset of the dataset by predicate.\\

    \noindent\textbf{Repsonse variable:} projection ratings scaled for beta-regression.\\

    \noindent\textbf{Fixed effect:} operator (modal, negation, question, conditional; with reference level: modal)\\

    \noindent\textbf{Random effects:} Item random intercepts and slopes by operator; No participant random effects, because each participant saw each predicate only once.\\

    \noindent The models were fit using \texttt{brms}
    % (\citealt{burkner_brms_2017}) in R (\citealt{r_core_team_r_2014}), 
    using low-information priors (\texttt{brms} defaults). The estimation used $4$ chains, $4,000$ iterations per chain, $700$ warm-up, total $13,200$ iterations saved for each model.

    \subsection{Model output}

    For each predicate, differences between levels of operator were established by considering the pairwise difference between estimated marginal means for each level of operator, using the ‘emmeans’ package (Lenth 2023) in R (R Core Team 2016). The below table gives posterior means, as well as upper and lower values for 95\% highest density intervals (HDIs) for the derived variables representing the pairwise differences.

    \begin{longtable}{llrrr}\toprule
     predicate & contrast & mean & lower & upper \\ \midrule
     acknowledge & conditional - negation & -0.50 & -0.70 & -0.31 \\ 
      acknowledge & conditional - question & 0.19 & -0.03 & 0.42 \\ 
      acknowledge & modal - conditional & -0.21 & -0.36 & -0.05 \\ 
      acknowledge & modal - negation & -0.71 & -0.90 & -0.50 \\ 
      acknowledge & modal - question & -0.01 & -0.23 & 0.21 \\ 
      acknowledge & negation - question & 0.69 & 0.44 & 0.97 \\ \midrule
      %
      admit & conditional - negation & 0.58 & 0.40 & 0.76 \\ 
      admit & conditional - question & 0.30 & 0.10 & 0.49 \\ 
      admit & modal - conditional & -0.50 & -0.67 & -0.33 \\ 
      admit & modal - negation & 0.08 & -0.08 & 0.22 \\ 
      admit & modal - question & -0.21 & -0.37 & -0.05 \\ 
      admit & negation - question & -0.28 & -0.46 & -0.12 \\ \midrule
      %
      announce & conditional - negation & 0.42 & 0.25 & 0.60 \\ 
      announce & conditional - question & 0.32 & 0.14 & 0.48 \\ 
      announce & modal - conditional & -0.48 & -0.63 & -0.34 \\ 
      announce & modal - negation & -0.06 & -0.23 & 0.11 \\ 
      announce & modal - question & -0.17 & -0.33 & -0.01 \\ 
      announce & negation - question & -0.11 & -0.29 & 0.07 \\ \midrule
      %
      be\_annoyed & conditional - negation & -0.59 & -0.77 & -0.41 \\ 
      be\_annoyed & conditional - question & -0.90 & -1.08 & -0.70 \\ 
      be\_annoyed & modal - conditional & -0.33 & -0.48 & -0.16 \\ 
      be\_annoyed & modal - negation & -0.92 & -1.08 & -0.76 \\ 
      be\_annoyed & modal - question & -1.23 & -1.40 & -1.05 \\ 
      be\_annoyed & negation - question & -0.31 & -0.50 & -0.12 \\ \midrule
      %
      be\_right & conditional - negation & -0.22 & -0.39 & -0.06 \\ 
      be\_right & conditional - question & 0.40 & 0.21 & 0.57 \\ 
      be\_right & modal - conditional & 0.43 & 0.28 & 0.58 \\ 
      be\_right & modal - negation & 0.21 & 0.05 & 0.37 \\ 
      be\_right & modal - question & 0.84 & 0.66 & 1.00 \\ 
      be\_right & negation - question & 0.62 & 0.43 & 0.81 \\ \midrule
      %
      confess & conditional - negation & 0.65 & 0.48 & 0.82 \\ 
      confess & conditional - question & 0.45 & 0.29 & 0.61 \\ 
      confess & modal - conditional & -0.62 & -0.77 & -0.48 \\ 
      confess & modal - negation & 0.03 & -0.14 & 0.18 \\ 
      confess & modal - question & -0.17 & -0.32 & -0.02 \\ 
      confess & negation - question & -0.20 & -0.38 & -0.03 \\ \midrule
      %
      confirm & conditional - negation & 0.77 & 0.59 & 0.95 \\ 
      confirm & conditional - question & 0.55 & 0.34 & 0.76 \\ 
      confirm & modal - conditional & 0.12 & -0.04 & 0.28 \\ 
      confirm & modal - negation & 0.89 & 0.73 & 1.05 \\ 
      confirm & modal - question & 0.67 & 0.48 & 0.85 \\ 
      confirm & negation - question & -0.22 & -0.42 & -0.02 \\ \midrule

      demonstrate & conditional - negation & 0.58 & 0.42 & 0.74 \\ 
      demonstrate & conditional - question & 0.21 & 0.06 & 0.36 \\ 
      demonstrate & modal - conditional & -0.17 & -0.31 & -0.03 \\ 
      demonstrate & modal - negation & 0.41 & 0.25 & 0.56 \\ 
      demonstrate & modal - question & 0.03 & -0.11 & 0.18 \\ 
      demonstrate & negation - question & -0.37 & -0.53 & -0.21 \\ \midrule

      discover & conditional - negation & 0.46 & 0.27 & 0.65 \\ 
      discover & conditional - question & -0.15 & -0.33 & 0.03 \\ 
      discover & modal - conditional & -0.64 & -0.79 & -0.48 \\ 
      discover & modal - negation & -0.18 & -0.36 & -0.01 \\ 
      discover & modal - question & -0.79 & -0.95 & -0.61 \\ 
      discover & negation - question & -0.61 & -0.81 & -0.42 \\ \midrule

      establish & conditional - negation & 0.44 & 0.26 & 0.62 \\ 
      establish & conditional - question & 0.28 & 0.10 & 0.47 \\ 
      establish & modal - conditional & -0.06 & -0.24 & 0.11 \\ 
      establish & modal - negation & 0.37 & 0.22 & 0.52 \\ 
      establish & modal - question & 0.22 & 0.07 & 0.37 \\ 
      establish & negation - question & -0.15 & -0.32 & 0.01 \\ \midrule

      hear & conditional - negation & 0.44 & 0.27 & 0.61 \\ 
      hear & conditional - question & -0.03 & -0.19 & 0.13 \\ 
      hear & modal - conditional & -0.92 & -1.06 & -0.76 \\ 
      hear & modal - negation & -0.47 & -0.63 & -0.31 \\ 
      hear & modal - question & -0.95 & -1.10 & -0.79 \\ 
      hear & negation - question & -0.47 & -0.65 & -0.31 \\ \midrule

      inform & conditional - negation & 0.12 & -0.07 & 0.30 \\ 
      inform & conditional - question & -0.33 & -0.53 & -0.13 \\ 
      inform & modal - conditional & -0.63 & -0.80 & -0.45 \\ 
      inform & modal - negation & -0.51 & -0.67 & -0.35 \\ 
      inform & modal - question & -0.96 & -1.12 & -0.79 \\ 
      inform & negation - question & -0.45 & -0.62 & -0.26 \\ \midrule

      know & conditional - negation & 0.13 & -0.06 & 0.31 \\ 
      know & conditional - question & -0.56 & -0.79 & -0.35 \\ 
      know & modal - conditional & -0.70 & -0.86 & -0.55 \\ 
      know & modal - negation & -0.57 & -0.74 & -0.40 \\ 
      know & modal - question & -1.26 & -1.49 & -1.04 \\ 
      know & negation - question & -0.70 & -0.93 & -0.46 \\ \midrule

      pretend & conditional - negation & -1.00 & -1.22 & -0.76 \\ 
      pretend & conditional - question & -0.09 & -0.33 & 0.12 \\ 
      pretend & modal - conditional & 0.20 & -0.03 & 0.42 \\ 
      pretend & modal - negation & -0.80 & -0.97 & -0.64 \\ 
      pretend & modal - question & 0.11 & -0.06 & 0.27 \\ 
      pretend & negation - question & 0.91 & 0.73 & 1.08 \\ \midrule

      prove & conditional - negation & 0.52 & 0.35 & 0.69 \\ 
      prove & conditional - question & 0.38 & 0.20 & 0.54 \\ 
      prove & modal - conditional & 0.24 & 0.09 & 0.40 \\ 
      prove & modal - negation & 0.77 & 0.61 & 0.92 \\ 
      prove & modal - question & 0.62 & 0.46 & 0.78 \\ 
      prove & negation - question & -0.15 & -0.33 & 0.02 \\ \midrule

      reveal & conditional - negation & 0.63 & 0.46 & 0.79 \\ 
      reveal & conditional - question & 0.29 & 0.10 & 0.49 \\ 
      reveal & modal - conditional & -0.60 & -0.77 & -0.45 \\ 
      reveal & modal - negation & 0.02 & -0.13 & 0.16 \\ 
      reveal & modal - question & -0.32 & -0.49 & -0.13 \\ 
      reveal & negation - question & -0.34 & -0.52 & -0.16 \\ \midrule

      say & conditional - negation & 0.30 & 0.04 & 0.54 \\ 
      say & conditional - question & 1.23 & 1.01 & 1.44 \\ 
      say & modal - conditional & -0.45 & -0.64 & -0.28 \\ 
      say & modal - negation & -0.16 & -0.36 & 0.05 \\ 
      say & modal - question & 0.77 & 0.59 & 0.95 \\ 
      say & negation - question & 0.93 & 0.73 & 1.14 \\ \midrule

      see & conditional - negation & 0.55 & 0.33 & 0.78 \\ 
      see & conditional - question & -0.15 & -0.35 & 0.08 \\ 
      see & modal - conditional & -0.89 & -1.09 & -0.67 \\ 
      see & modal - negation & -0.33 & -0.50 & -0.17 \\ 
      see & modal - question & -1.03 & -1.20 & -0.87 \\ 
      see & negation - question & -0.70 & -0.89 & -0.52 \\ \midrule

      suggest & conditional - negation & 0.25 & 0.08 & 0.42 \\ 
      suggest & conditional - question & 0.61 & 0.44 & 0.77 \\ 
      suggest & modal - conditional & -0.27 & -0.42 & -0.11 \\ 
      suggest & modal - negation & -0.02 & -0.19 & 0.14 \\ 
      suggest & modal - question & 0.34 & 0.18 & 0.49 \\ 
      suggest & negation - question & 0.36 & 0.19 & 0.52 \\ \midrule

      think & conditional - negation & -0.50 & -0.70 & -0.30 \\ 
      think & conditional - question & 0.19 & -0.04 & 0.41 \\ 
      think & modal - conditional & -0.21 & -0.36 & -0.05 \\ 
      think & modal - negation & -0.71 & -0.91 & -0.52 \\ 
      think & modal - question & -0.01 & -0.24 & 0.22 \\ 
      think & negation - question & 0.70 & 0.44 & 0.97 \\ 
      \end{longtable}

\bibliographystyle{sub-chicago}
\bibliography{projection.bib}
\end{document}
